### 2020-02-22 s1_text/s1_text.tex
Add few lines to SI on expt methods

\section{Experimental materials and methods} \label{sec:exp}

\textcolor{red}{missing}

>>>>

\section{Experimental materials and methods} \label{sec:exp}
Strains used in this work derive from \emph{E.\ coli} K12 MG1655 with
the \emph{lac} operon removed and were constructed similarly to those
used in~\cite{RazoMejia2018}. The YFP-expressing reporter constructs
were cloned into a pZS25 backbone with kanamycin resistance and
integrated at the \emph{galK} locus using recombineering.
\textDelta\emph{xapAB} and \textDelta\emph{xapABR} knockouts were
generated \textbf{???using P1 transduction from the Keio collection???}

Flow cytometry measurements, as well as growth and preparation of cell
cultures, were carried out as in~\cite{RazoMejia2018}.

\textbf{??What else needs adding here??}
